Ensembler: Enabling high-throughput molecular simulations at the superfamily scale

### 2015-03-22 manuscript/ms.tex
For some reason, document was structures as section -> subsubsection. Fixed this so it is section -> subsection -> subsubsection.

\subsubsection*{Target selection and retrieval}

@@

\subsubsection*{Template selection and retrieval}

@@

\subsubsection*{Template refinement}

@@

\subsubsection*{Modeling}

@@

\subsubsection*{Filtering of nearly identical models}

@@

\subsubsection*{Refinement of models}

@@

\subsubsection*{Solvation and NPT equilibration}

@@

\subsubsection*{Packaging}

{\bf Ensembler} provides a packaging module which can be used to compress models in preparation for data transfer, or to prepare models with the appropriate directory and file structure for subsequent production simulations on the distributed computing platform Folding@home (CITE: F@H).
The module could be easily extended to add methods for preparing models for use with other software, such as the Copernicus platform for running automated, distributed MD simulations.
{\color{red}[JDC: Is there a way we can make this more generally useful to others?  For example, is there a different system they might want to use, such as \href{http://copernicus.readthedocs.org/en/latest/tutorials/md-tutorial.html#creating-a-workflow-for-molecular-simulations}{Copernicus}?]}
{\color{blue}[DLP: addressed]}

\subsubsection*{Provenance}

@@

\subsubsection*{Modeling of all human tyrosine kinase catalytic domains}

@@

\subsubsection*{Ensembler modeling statistics}

@@

Following loop remodeling, the {\bf Ensembler} pipeline was performed up to and including the implicit solvent MD refinement stage, which completed with \num{373513} (94\%) surviving models.
To obtain statistics for the solvation stage without generating a sizeable amount of coordinate data, the {\tt solvate} subcommand was performed for two representative individual kinases (\emph{Src} and \emph{Abl1}).
The number of models which survived each stage are shown in Fig.~\ref{figpipeline}, indicating that the greatest attrition occurred during the modeling stage.
The number of refined models for each target ranged from 4005 to 4248, with a median of 4160 and standard deviation of 60.
Fig.~\ref{figpipeline} also indicates the typical timing achieved on a cluster for each stage, showing that the {\tt build\_models} and {\tt refine\_implicit\_md} stages are by far the most compute-intensive.

@@

\subsubsection*{Evaluation of model quality and utility}

@@

@@

@@

\subsubsection*{Availability}

@@

\subsubsection*{Future Directions}

@@

\subsubsection*{Conclusion}

>>>>

\subsection*{Target selection and retrieval}

@@

\subsection*{Template selection and retrieval}

@@

\subsection*{Template refinement}

@@

\subsection*{Modeling}

@@

\subsection*{Filtering of nearly identical models}

@@

\subsection*{Refinement of models}

@@

\subsection*{Solvation and NPT equilibration}

@@

\subsection*{Packaging}

{\bf Ensembler} provides a packaging module which can be used to compress models in preparation for data transfer, or to prepare models with the appropriate directory and file structure for subsequent production simulations on the distributed computing platform Folding@home {\color{red}[CITE: F@H]}.
The module could be easily extended to add methods for preparing models for use with other software, such as the Copernicus platform for running automated, distributed MD simulations.
{\color{red}[JDC: Is there a way we can make this more generally useful to others?  For example, is there a different system they might want to use, such as \href{http://copernicus.readthedocs.org/en/latest/tutorials/md-tutorial.html#creating-a-workflow-for-molecular-simulations}{Copernicus}?]}
{\color{blue}[DLP: addressed]}
{\color{red}[JDC: How was this addressed?]}

\subsection*{Other features}

\subsubsection*{Tracking provenance information}

@@

\subsection*{Modeling of all human tyrosine kinase catalytic domains}

@@

\subsection*{Ensembler modeling statistics}

@@

Following loop remodeling, the {\bf Ensembler} pipeline was performed up to and including the implicit solvent MD refinement stage, which completed with \num{373513} (94\%) surviving models across all TKs.
To obtain statistics for the solvation stage without generating a sizeable amount of coordinate data {\color{red}[JDC: State how big the solvated model PDBs are?]}, the {\tt solvate} subcommand was performed for two representative individual kinases (\emph{Src} and \emph{Abl1}).

The number of models which survived each stage are shown in Fig.~\ref{figpipeline}, indicating that the greatest attrition occurred during the modeling stage.
The number of refined models for each target ranged from \num{4005} to \num{4248}, with a median of \num{4160} and standard deviation of \num{60}.
Fig.~\ref{figpipeline} also indicates the typical timing achieved on a cluster for each stage, showing that the {\tt build\_models} and {\tt refine\_implicit\_md} stages are by far the most compute-intensive.

@@

\subsection*{Evaluation of model quality and utility}

@@

\subsubsection*{All tyrosine kinases}

@@

\subsubsection*{Src and Abl1}

@@

\subsection*{Availability}

@@

\subsection*{Future Directions}

@@

\subsection*{Conclusion}
